Collision rates of planetesimals near mean-motion resonances

### 2021-01-26 main.tex
Clean up newlines and indentation in tex file

\noindent\textbf{where $v_{k}$ is the local Keplerian velocity. The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to gravitational focusing. When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric value. An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$. For small $v$, gravitational focusing facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly supressed. This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}

@@

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. \textbf{This timescale must be resolved in order to properly follow close gravitational encounters between these bodies}. To 
resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time stepping scheme, following
\citep{2015ApJ...806...23L}. 
To start, all bodies are placed on the base time step. A first pass of collision detection is then run in 
which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are 
placed on a time step that is a factor of 16 smaller than the orbital
time step. Although this is still a factor of roughly 7 larger than the dynamical time of a planetesimal, we found no difference in the collision rate
when using any smaller of a minimum time step size.
The purpose of the two-tiered scheme is to properly resolve 
the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.

>>>>

\noindent\textbf{where $v_{k}$ is the local Keplerian velocity. The second term in equation \ref{eq:saf} can be thought of as an additional enhancement to the collision cross section due to 
gravitational focusing. When the typical encounter velocity is small compared to the mutual escape velocity of the planetesimals, the collision cross section greatly exceeds the geometric 
value. An important feature of equation \ref{eq:saf} is that for a fixed value of $n$, the collision rate exhibits a global minimum as a function of $v$. For small $v$, gravitational focusing 
facilitates more collisions, while for large $v$ the encounter rate simply becomes so great that the collision rate again increases, even though gravitational focusing is mostly surpressed. 
This point will become relevant in section \ref{sec:vary_ecc} when we examine the qualitative changes in the collision rate near mean-motion resonances.}

@@

An additional timescale is set by the dynamical time of the planetesimals ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. \textbf{This timescale must be resolved in order to properly 
follow close gravitational encounters between these bodies}. To resolve the base time step and the dynamical timescale of planetesimals simultaneously, we use a two-tiered time 
stepping scheme, following\citep{2015ApJ...806...23L}. To start, all bodies are placed on the base time step. A first pass of collision detection is then run in which the radii of all bodies are 
inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than the orbital time step. Although 
this is still a factor of roughly 7 larger than the dynamical time of a planetesimal, we found no difference in the collision rate when using any smaller of a minimum time step size.The 
purpose of the two-tiered scheme is to properly resolve the gravitational interactions between any bodies that undergo a close encounter. This prevents the coarser base time step from 
reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
